COVID-19 Vaccine Acceptance and Hesitancy in Low and Middle Income Countries

### 2021-06-22 paper_files/figure-latex/fig3paper-1.tex
update

% Created by tikzDevice version 0.12.3.1 on 2021-05-04 13:13:00
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (722.70,650.43);
\end{scope}
\begin{scope}
\path[clip] ( 48.28,541.57) rectangle (371.71,627.77);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 48.28,541.57) rectangle (371.71,627.77);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,556.45) --
	(371.71,556.45);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,578.39) --
	(371.71,578.39);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,600.33) --
	(371.71,600.33);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,622.27) --
	(371.71,622.27);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,545.48) --
	(371.71,545.48);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,567.42) --
	(371.71,567.42);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,589.36) --
	(371.71,589.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,611.30) --
	(371.71,611.30);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.24,541.57) --
	( 75.24,627.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (120.16,541.57) --
	(120.16,627.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (165.08,541.57) --
	(165.08,627.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (209.99,541.57) --
	(209.99,627.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (254.91,541.57) --
	(254.91,627.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (299.83,541.57) --
	(299.83,627.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (344.75,541.57) --
	(344.75,627.77);
\definecolor{fillColor}{RGB}{221,204,119}

\path[fill=fillColor] (144.86,545.48) rectangle (185.29,561.63);

\path[fill=fillColor] (234.70,545.48) rectangle (275.13,547.15);

\path[fill=fillColor] (189.78,545.48) rectangle (230.21,547.06);

\path[fill=fillColor] (279.62,545.48) rectangle (320.05,555.66);

\path[fill=fillColor] (324.54,545.48) rectangle (364.97,546.98);

\path[fill=fillColor] ( 55.02,545.48) rectangle ( 95.45,590.77);

\path[fill=fillColor] ( 99.94,545.48) rectangle (140.37,556.81);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 48.28,541.57) rectangle (371.71,627.77);
\end{scope}
\begin{scope}
\path[clip] ( 48.28,449.86) rectangle (371.71,536.07);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 48.28,449.86) rectangle (371.71,536.07);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,464.75) --
	(371.71,464.75);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,486.69) --
	(371.71,486.69);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,508.63) --
	(371.71,508.63);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,530.57) --
	(371.71,530.57);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,453.78) --
	(371.71,453.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,475.72) --
	(371.71,475.72);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,497.66) --
	(371.71,497.66);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,519.60) --
	(371.71,519.60);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.24,449.86) --
	( 75.24,536.07);

\path[draw=drawColor,line width= 0.6pt,line join=round] (120.16,449.86) --
	(120.16,536.07);

\path[draw=drawColor,line width= 0.6pt,line join=round] (165.08,449.86) --
	(165.08,536.07);

\path[draw=drawColor,line width= 0.6pt,line join=round] (209.99,449.86) --
	(209.99,536.07);

\path[draw=drawColor,line width= 0.6pt,line join=round] (254.91,449.86) --
	(254.91,536.07);

\path[draw=drawColor,line width= 0.6pt,line join=round] (299.83,449.86) --
	(299.83,536.07);

\path[draw=drawColor,line width= 0.6pt,line join=round] (344.75,449.86) --
	(344.75,536.07);
\definecolor{fillColor}{RGB}{221,204,119}

\path[fill=fillColor] (144.86,453.78) rectangle (185.29,485.02);

\path[fill=fillColor] (234.70,453.78) rectangle (275.13,454.13);

\path[fill=fillColor] (189.78,453.78) rectangle (230.21,467.91);

\path[fill=fillColor] (279.62,453.78) rectangle (320.05,454.22);

\path[fill=fillColor] (324.54,453.78) rectangle (364.97,455.88);

\path[fill=fillColor] ( 55.02,453.78) rectangle ( 95.45,492.57);

\path[fill=fillColor] ( 99.94,453.78) rectangle (140.37,454.48);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 48.28,449.86) rectangle (371.71,536.07);
\end{scope}
\begin{scope}
\path[clip] ( 48.28,358.15) rectangle (371.71,444.36);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 48.28,358.15) rectangle (371.71,444.36);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,373.04) --
	(371.71,373.04);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,394.98) --
	(371.71,394.98);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,416.92) --
	(371.71,416.92);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,438.86) --
	(371.71,438.86);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,362.07) --
	(371.71,362.07);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,384.01) --
	(371.71,384.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,405.95) --
	(371.71,405.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,427.89) --
	(371.71,427.89);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.24,358.15) --
	( 75.24,444.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] (120.16,358.15) --
	(120.16,444.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] (165.08,358.15) --
	(165.08,444.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] (209.99,358.15) --
	(209.99,444.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] (254.91,358.15) --
	(254.91,444.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] (299.83,358.15) --
	(299.83,444.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] (344.75,358.15) --
	(344.75,444.36);
\definecolor{fillColor}{RGB}{221,204,119}

\path[fill=fillColor] (144.86,362.07) rectangle (185.29,375.24);

\path[fill=fillColor] (234.70,362.07) rectangle (275.13,362.60);

\path[fill=fillColor] (189.78,362.07) rectangle (230.21,363.04);

\path[fill=fillColor] (279.62,362.07) rectangle (320.05,391.21);

\path[fill=fillColor] (324.54,362.07) rectangle (364.97,362.42);

\path[fill=fillColor] ( 55.02,362.07) rectangle ( 95.45,382.26);

\path[fill=fillColor] ( 99.94,362.07) rectangle (140.37,385.50);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 48.28,358.15) rectangle (371.71,444.36);
\end{scope}
\begin{scope}
\path[clip] ( 48.28,266.45) rectangle (371.71,352.65);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 48.28,266.45) rectangle (371.71,352.65);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,281.33) --
	(371.71,281.33);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,303.27) --
	(371.71,303.27);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,325.21) --
	(371.71,325.21);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,347.15) --
	(371.71,347.15);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,270.36) --
	(371.71,270.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,292.30) --
	(371.71,292.30);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,314.24) --
	(371.71,314.24);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,336.18) --
	(371.71,336.18);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.24,266.45) --
	( 75.24,352.65);

\path[draw=drawColor,line width= 0.6pt,line join=round] (120.16,266.45) --
	(120.16,352.65);

\path[draw=drawColor,line width= 0.6pt,line join=round] (165.08,266.45) --
	(165.08,352.65);

\path[draw=drawColor,line width= 0.6pt,line join=round] (209.99,266.45) --
	(209.99,352.65);

\path[draw=drawColor,line width= 0.6pt,line join=round] (254.91,266.45) --
	(254.91,352.65);

\path[draw=drawColor,line width= 0.6pt,line join=round] (299.83,266.45) --
	(299.83,352.65);

\path[draw=drawColor,line width= 0.6pt,line join=round] (344.75,266.45) --
	(344.75,352.65);
\definecolor{fillColor}{RGB}{221,204,119}

\path[fill=fillColor] (144.86,270.36) rectangle (185.29,273.09);

\path[fill=fillColor] (234.70,270.36) rectangle (275.13,270.36);

\path[fill=fillColor] (189.78,270.36) rectangle (230.21,271.86);

\path[fill=fillColor] (279.62,270.36) rectangle (320.05,275.46);

\path[fill=fillColor] ( 55.02,270.36) rectangle ( 95.45,348.73);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 48.28,266.45) rectangle (371.71,352.65);
\end{scope}
\begin{scope}
\path[clip] ( 48.28,174.74) rectangle (371.71,260.95);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 48.28,174.74) rectangle (371.71,260.95);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,189.63) --
	(371.71,189.63);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,211.57) --
	(371.71,211.57);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,233.51) --
	(371.71,233.51);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,255.45) --
	(371.71,255.45);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,178.66) --
	(371.71,178.66);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,200.60) --
	(371.71,200.60);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,222.54) --
	(371.71,222.54);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,244.48) --
	(371.71,244.48);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.24,174.74) --
	( 75.24,260.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (120.16,174.74) --
	(120.16,260.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (165.08,174.74) --
	(165.08,260.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (209.99,174.74) --
	(209.99,260.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (254.91,174.74) --
	(254.91,260.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (299.83,174.74) --
	(299.83,260.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (344.75,174.74) --
	(344.75,260.95);
\definecolor{fillColor}{RGB}{221,204,119}

\path[fill=fillColor] (144.86,178.66) rectangle (185.29,193.40);

\path[fill=fillColor] (234.70,178.66) rectangle (275.13,179.97);

\path[fill=fillColor] (189.78,178.66) rectangle (230.21,183.31);

\path[fill=fillColor] (279.62,178.66) rectangle (320.05,187.96);

\path[fill=fillColor] (324.54,178.66) rectangle (364.97,180.76);

\path[fill=fillColor] ( 55.02,178.66) rectangle ( 95.45,220.87);

\path[fill=fillColor] ( 99.94,178.66) rectangle (140.37,195.60);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 48.28,174.74) rectangle (371.71,260.95);
\end{scope}
\begin{scope}
\path[clip] ( 48.28, 83.03) rectangle (371.71,169.24);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 48.28, 83.03) rectangle (371.71,169.24);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28, 97.92) --
	(371.71, 97.92);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,119.86) --
	(371.71,119.86);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,141.80) --
	(371.71,141.80);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,163.74) --
	(371.71,163.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28, 86.95) --
	(371.71, 86.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,108.89) --
	(371.71,108.89);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,130.83) --
	(371.71,130.83);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,152.77) --
	(371.71,152.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.24, 83.03) --
	( 75.24,169.24);

\path[draw=drawColor,line width= 0.6pt,line join=round] (120.16, 83.03) --
	(120.16,169.24);

\path[draw=drawColor,line width= 0.6pt,line join=round] (165.08, 83.03) --
	(165.08,169.24);

\path[draw=drawColor,line width= 0.6pt,line join=round] (209.99, 83.03) --
	(209.99,169.24);

\path[draw=drawColor,line width= 0.6pt,line join=round] (254.91, 83.03) --
	(254.91,169.24);

\path[draw=drawColor,line width= 0.6pt,line join=round] (299.83, 83.03) --
	(299.83,169.24);

\path[draw=drawColor,line width= 0.6pt,line join=round] (344.75, 83.03) --
	(344.75,169.24);
\definecolor{fillColor}{RGB}{221,204,119}

\path[fill=fillColor] (144.86, 86.95) rectangle (185.29, 97.04);

\path[fill=fillColor] (189.78, 86.95) rectangle (230.21, 89.06);

\path[fill=fillColor] (279.62, 86.95) rectangle (320.05,106.17);

\path[fill=fillColor] (324.54, 86.95) rectangle (364.97, 87.04);

\path[fill=fillColor] ( 55.02, 86.95) rectangle ( 95.45,117.23);

\path[fill=fillColor] ( 99.94, 86.95) rectangle (140.37,113.02);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 48.28, 83.03) rectangle (371.71,169.24);
\end{scope}
\begin{scope}
\path[clip] (393.78,541.57) rectangle (717.20,627.77);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (393.78,541.57) rectangle (717.20,627.77);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,556.45) --
	(717.20,556.45);

>>>>

% Created by tikzDevice version 0.12.3.1 on 2021-06-22 11:48:27
% !TEX encoding = UTF-8 Unicode
% !TEX program = xelatex

\documentclass[fontsize=7pt,DIV=calc]{scrartcl}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (722.70,650.43);
\end{scope}
\begin{scope}
\path[clip] ( 41.25,541.96) rectangle (369.36,631.27);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 41.25,541.96) rectangle (369.36,631.27);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,557.39) --
	(369.36,557.39);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,580.12) --
	(369.36,580.12);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,602.85) --
	(369.36,602.85);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,625.57) --
	(369.36,625.57);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,546.02) --
	(369.36,546.02);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,568.75) --
	(369.36,568.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,591.48) --
	(369.36,591.48);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,614.21) --
	(369.36,614.21);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 68.60,541.96) --
	( 68.60,631.27);

\path[draw=drawColor,line width= 0.6pt,line join=round] (114.17,541.96) --
	(114.17,631.27);

\path[draw=drawColor,line width= 0.6pt,line join=round] (159.74,541.96) --
	(159.74,631.27);

\path[draw=drawColor,line width= 0.6pt,line join=round] (205.31,541.96) --
	(205.31,631.27);

\path[draw=drawColor,line width= 0.6pt,line join=round] (250.88,541.96) --
	(250.88,631.27);

\path[draw=drawColor,line width= 0.6pt,line join=round] (296.45,541.96) --
	(296.45,631.27);

\path[draw=drawColor,line width= 0.6pt,line join=round] (342.02,541.96) --
	(342.02,631.27);
\definecolor{fillColor}{RGB}{221,204,119}

\path[fill=fillColor] (139.23,546.02) rectangle (180.24,562.75);

\path[fill=fillColor] (230.37,546.02) rectangle (271.38,547.75);

\path[fill=fillColor] (184.80,546.02) rectangle (225.81,547.66);

\path[fill=fillColor] (275.94,546.02) rectangle (316.95,556.57);

\path[fill=fillColor] (321.51,546.02) rectangle (362.52,547.57);

\path[fill=fillColor] ( 48.09,546.02) rectangle ( 89.10,592.94);

\path[fill=fillColor] ( 93.66,546.02) rectangle (134.67,557.75);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 41.25,541.96) rectangle (369.36,631.27);
\end{scope}
\begin{scope}
\path[clip] ( 41.25,447.16) rectangle (369.36,536.46);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 41.25,447.16) rectangle (369.36,536.46);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,462.58) --
	(369.36,462.58);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,485.31) --
	(369.36,485.31);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,508.04) --
	(369.36,508.04);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,530.77) --
	(369.36,530.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,451.22) --
	(369.36,451.22);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,473.95) --
	(369.36,473.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,496.67) --
	(369.36,496.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,519.40) --
	(369.36,519.40);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 68.60,447.16) --
	( 68.60,536.46);

\path[draw=drawColor,line width= 0.6pt,line join=round] (114.17,447.16) --
	(114.17,536.46);

\path[draw=drawColor,line width= 0.6pt,line join=round] (159.74,447.16) --
	(159.74,536.46);

\path[draw=drawColor,line width= 0.6pt,line join=round] (205.31,447.16) --
	(205.31,536.46);

\path[draw=drawColor,line width= 0.6pt,line join=round] (250.88,447.16) --
	(250.88,536.46);

\path[draw=drawColor,line width= 0.6pt,line join=round] (296.45,447.16) --
	(296.45,536.46);

\path[draw=drawColor,line width= 0.6pt,line join=round] (342.02,447.16) --
	(342.02,536.46);
\definecolor{fillColor}{RGB}{221,204,119}

\path[fill=fillColor] (139.23,451.22) rectangle (180.24,483.58);

\path[fill=fillColor] (230.37,451.22) rectangle (271.38,451.58);

\path[fill=fillColor] (184.80,451.22) rectangle (225.81,465.85);

\path[fill=fillColor] (275.94,451.22) rectangle (316.95,451.67);

\path[fill=fillColor] (321.51,451.22) rectangle (362.52,453.40);

\path[fill=fillColor] ( 48.09,451.22) rectangle ( 89.10,491.40);

\path[fill=fillColor] ( 93.66,451.22) rectangle (134.67,451.94);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 41.25,447.16) rectangle (369.36,536.46);
\end{scope}
\begin{scope}
\path[clip] ( 41.25,352.35) rectangle (369.36,441.66);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 41.25,352.35) rectangle (369.36,441.66);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,367.78) --
	(369.36,367.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,390.50) --
	(369.36,390.50);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,413.23) --
	(369.36,413.23);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,435.96) --
	(369.36,435.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,356.41) --
	(369.36,356.41);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,379.14) --
	(369.36,379.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,401.87) --
	(369.36,401.87);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,424.60) --
	(369.36,424.60);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 68.60,352.35) --
	( 68.60,441.66);

\path[draw=drawColor,line width= 0.6pt,line join=round] (114.17,352.35) --
	(114.17,441.66);

\path[draw=drawColor,line width= 0.6pt,line join=round] (159.74,352.35) --
	(159.74,441.66);

\path[draw=drawColor,line width= 0.6pt,line join=round] (205.31,352.35) --
	(205.31,441.66);

\path[draw=drawColor,line width= 0.6pt,line join=round] (250.88,352.35) --
	(250.88,441.66);

\path[draw=drawColor,line width= 0.6pt,line join=round] (296.45,352.35) --
	(296.45,441.66);

\path[draw=drawColor,line width= 0.6pt,line join=round] (342.02,352.35) --
	(342.02,441.66);
\definecolor{fillColor}{RGB}{221,204,119}

\path[fill=fillColor] (139.23,356.41) rectangle (180.24,370.05);

\path[fill=fillColor] (230.37,356.41) rectangle (271.38,356.96);

\path[fill=fillColor] (184.80,356.41) rectangle (225.81,357.41);

\path[fill=fillColor] (275.94,356.41) rectangle (316.95,386.59);

\path[fill=fillColor] (321.51,356.41) rectangle (362.52,356.77);

\path[fill=fillColor] ( 48.09,356.41) rectangle ( 89.10,377.32);

\path[fill=fillColor] ( 93.66,356.41) rectangle (134.67,380.69);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 41.25,352.35) rectangle (369.36,441.66);
\end{scope}
\begin{scope}
\path[clip] ( 41.25,257.55) rectangle (369.36,346.85);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 41.25,257.55) rectangle (369.36,346.85);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,272.97) --
	(369.36,272.97);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,295.70) --
	(369.36,295.70);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,318.43) --
	(369.36,318.43);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,341.16) --
	(369.36,341.16);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,261.60) --
	(369.36,261.60);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,284.33) --
	(369.36,284.33);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,307.06) --
	(369.36,307.06);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,329.79) --
	(369.36,329.79);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 68.60,257.55) --
	( 68.60,346.85);

\path[draw=drawColor,line width= 0.6pt,line join=round] (114.17,257.55) --
	(114.17,346.85);

\path[draw=drawColor,line width= 0.6pt,line join=round] (159.74,257.55) --
	(159.74,346.85);

\path[draw=drawColor,line width= 0.6pt,line join=round] (205.31,257.55) --
	(205.31,346.85);

\path[draw=drawColor,line width= 0.6pt,line join=round] (250.88,257.55) --
	(250.88,346.85);

\path[draw=drawColor,line width= 0.6pt,line join=round] (296.45,257.55) --
	(296.45,346.85);

\path[draw=drawColor,line width= 0.6pt,line join=round] (342.02,257.55) --
	(342.02,346.85);
\definecolor{fillColor}{RGB}{221,204,119}

\path[fill=fillColor] (139.23,261.60) rectangle (180.24,264.42);

\path[fill=fillColor] (230.37,261.60) rectangle (271.38,261.60);

\path[fill=fillColor] (184.80,261.60) rectangle (225.81,263.15);

\path[fill=fillColor] (275.94,261.60) rectangle (316.95,266.88);

\path[fill=fillColor] ( 48.09,261.60) rectangle ( 89.10,342.79);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 41.25,257.55) rectangle (369.36,346.85);
\end{scope}
\begin{scope}
\path[clip] ( 41.25,162.74) rectangle (369.36,252.05);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 41.25,162.74) rectangle (369.36,252.05);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,178.16) --
	(369.36,178.16);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,200.89) --
	(369.36,200.89);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,223.62) --
	(369.36,223.62);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,246.35) --
	(369.36,246.35);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,166.80) --
	(369.36,166.80);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,189.53) --
	(369.36,189.53);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,212.26) --
	(369.36,212.26);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,234.98) --
	(369.36,234.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 68.60,162.74) --
	( 68.60,252.05);

\path[draw=drawColor,line width= 0.6pt,line join=round] (114.17,162.74) --
	(114.17,252.05);

\path[draw=drawColor,line width= 0.6pt,line join=round] (159.74,162.74) --
	(159.74,252.05);

\path[draw=drawColor,line width= 0.6pt,line join=round] (205.31,162.74) --
	(205.31,252.05);

\path[draw=drawColor,line width= 0.6pt,line join=round] (250.88,162.74) --
	(250.88,252.05);

\path[draw=drawColor,line width= 0.6pt,line join=round] (296.45,162.74) --
	(296.45,252.05);

\path[draw=drawColor,line width= 0.6pt,line join=round] (342.02,162.74) --
	(342.02,252.05);
\definecolor{fillColor}{RGB}{221,204,119}

\path[fill=fillColor] (139.23,166.80) rectangle (180.24,182.07);

\path[fill=fillColor] (230.37,166.80) rectangle (271.38,168.16);

\path[fill=fillColor] (184.80,166.80) rectangle (225.81,171.62);

\path[fill=fillColor] (275.94,166.80) rectangle (316.95,176.44);

\path[fill=fillColor] (321.51,166.80) rectangle (362.52,168.98);

\path[fill=fillColor] ( 48.09,166.80) rectangle ( 89.10,210.53);

\path[fill=fillColor] ( 93.66,166.80) rectangle (134.67,184.34);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 41.25,162.74) rectangle (369.36,252.05);
\end{scope}
\begin{scope}
\path[clip] ( 41.25, 67.93) rectangle (369.36,157.24);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 41.25, 67.93) rectangle (369.36,157.24);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25, 83.36) --
	(369.36, 83.36);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,106.09) --
	(369.36,106.09);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,128.81) --
	(369.36,128.81);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,151.54) --
	(369.36,151.54);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25, 71.99) --
	(369.36, 71.99);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25, 94.72) --
	(369.36, 94.72);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,117.45) --
	(369.36,117.45);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,140.18) --
	(369.36,140.18);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 68.60, 67.93) --
	( 68.60,157.24);

\path[draw=drawColor,line width= 0.6pt,line join=round] (114.17, 67.93) --
	(114.17,157.24);

\path[draw=drawColor,line width= 0.6pt,line join=round] (159.74, 67.93) --
	(159.74,157.24);

\path[draw=drawColor,line width= 0.6pt,line join=round] (205.31, 67.93) --
	(205.31,157.24);

\path[draw=drawColor,line width= 0.6pt,line join=round] (250.88, 67.93) --
	(250.88,157.24);

\path[draw=drawColor,line width= 0.6pt,line join=round] (296.45, 67.93) --
	(296.45,157.24);

\path[draw=drawColor,line width= 0.6pt,line join=round] (342.02, 67.93) --
	(342.02,157.24);
\definecolor{fillColor}{RGB}{221,204,119}

\path[fill=fillColor] (139.23, 71.99) rectangle (180.24, 82.45);

\path[fill=fillColor] (184.80, 71.99) rectangle (225.81, 74.17);

\path[fill=fillColor] (275.94, 71.99) rectangle (316.95, 91.90);

\path[fill=fillColor] (321.51, 71.99) rectangle (362.52, 72.08);

\path[fill=fillColor] ( 48.09, 71.99) rectangle ( 89.10,103.36);

\path[fill=fillColor] ( 93.66, 71.99) rectangle (134.67, 98.99);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 41.25, 67.93) rectangle (369.36,157.24);
\end{scope}
\begin{scope}
\path[clip] (389.10,541.96) rectangle (717.20,631.27);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (389.10,541.96) rectangle (717.20,631.27);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] (389.10,557.39) --
	(717.20,557.39);
